From clusters to queries: exploiting uncertainty in the modularity landscape of complex networks

### 2018-04-24 article/article.tex
Tidyup, figure, refs

\author{John King}
\affiliation{%
  \institution{School of Mathematical Sciences}
  \streetaddress{University of Nottingham}
  \city{Nottingham}
  \country{United Kingdom}
  \postcode{NG7 2RD}
}
\email{john.king@nottingham.ac.uk}

\begin{abstract}
Uncovering latent community structure in complex networks is a field that has received an enormous amount of attention.
Unfortunately, whilst potentially very powerful unsupervised methods for classifying nodes into similar groups based on topology alone has been shown to have several major limitations.
Crucially, the search space for module extraction approaches appears to be extremely glassy, with many high valued solutions that lack any real similarity to one another.
However, in this paper we argue that this is not a flaw with the modularity maximisation algorithm but, rather, information that can be used to aid the classification of functional relationships between vertices.
Formally, we present an approach to generating a search ``index'' for a network, based on the space of high value modular partitions.
This search spaces allows the formulation of query based measures that provide a score for the level of relatedness to a given labelled query set.
The methods developed in this paper are applied to biological and social datasets with ground-truth label data, with very small query sets for nodes.
When tested on both real and synthetic datasets our method achieves extremely high levels of classification.
Furthermore, the approach can be applied in distributed environments potentially allowing it to scale to very large networks.
\end{abstract}

@@

A fundamental issue at the heart of machine learning methods applied to large scale datasets is the ability to correctly identify classes of related objects in an unsupervised manner.
In network science, this methodology is often referred to as \textit{community} detection, due to the intuitive analogy from the social sciences \cite{fortunato2010community}.
Many algorithms exist to solve this problem, yet initial starting conditions or different optimisation strategies may result in conflicting results even when the same objective function is being maximised \cite{good2010performance}.
In this paper, we develop an intuitive method to use the uncertainty amongst a high number of near optimal solutions to meaedsure the overall quality of a given labelling scheme that can come from classes known \textit{a-priori} or clusters detected through other methods.
This approach also allows the expansion of labels to find potentially related vertices to an initial starting subset.

The number and size of communities is, generally, not known \textit{a priori}, and the problem has been shown to be NP-hard \cite{npHardModularity}.
The work of Good \textit{et al.} \cite{good2010performance} recently highlighted that the popular modularity maximisation algorithm has a highly ``glassy'' search space.
In this situation there are many locally optimal partitions that bear little to no resemblance to each other by measure of mutual information.
This allows greedy optimisation algorithms \cite{blondel2008fast} to trivially find solutions that score extremely high values of modularity.
In order to solve this issue, certain approaches use a consensus based approach to clustering, combining many high value partitions into a given median partition.

The use of community detection is widespread.
For example, core goal in systems biology is to characterise the function and functional relationships between genes, proteins or metabolites within a larger network \cite{}.
In many situations, only the role of a small number of genes is known, with much of the annotation for a given organism being computed through naive homology information that ignores the role of a gene within a wider context.
The advent of high throughput experimental datasets has allowed the construction of genome scale networks, leading to the observation of non-trivial topological properties such as densely connected clusters \cite{ArabidopsisConsortium2011}.
These densely connected clusters are widely believed to be associated with specific function, such as protein complexes or biochemical pathways \cite{}.

@@

In this paper, we do not seek to find a single ``best'' partition, either overlapping or not.
Instead, we use the large number of highly modular solutions to form the index for a search query system.
In essence, this is a method of semi-supervised learning that attempts to find items related given labelled sets of vertices using topology alone.
Each high value partition, if statistically more modular than random, can be treated as information about the relationships between vertices.
As the objective of community detection approaches is to relate information, it is assumed that some labelled meta-data can be used to find unlabelled, potentially related vertices.
The overall objective can be thought of as a form of recommender system \cite{ricci2011introduction}, relating a given query in the form of a vertex set to potentially related information by exploiting the co-occurrence between communities.

In this vein, we apply the method presented in this paper to the problem of classifying biological function.
The objective of our algorithm, in this sense, is given sets of known function for genes or proteins within interaction networks, to generate meaningful hypothesis that can be externally validated.
Naturally this process depends heavily on the quality of underlying datasets, however, we feel this approach is a conceptual change from conventional module detection approaches which only consider a single clustering of a network, overlapping or not, where only binary classification is considered.

We propose an algorithm that pre-computes an index of clusterings for a given complex network, based on the fast greedy Louvain algorithm \cite{blondel2008fast}, used in a distributed manner.
The detected clusters then form the basis of a searching algorithm that allows one to compute the relatedness of subsets of nodes.
The querying method is a polynomial time algorithm that could be trivially adapted to form the basis of many user facing applications.
This approach is applied to a number of real world metabolic and protein interaction datasets with explicit queries relating to biological function.
In addition, the ranking scores for the uncertainty of community classification are used to capture critical ``bridge'' nodes and edges allowing an efficient multi-scale form of visualisation for networks with glassy modular structure.

\section{Vertex classification}
The intuitive notion that the structure of a vertex's connections gives insight into its function is a fundamental basis for research in network science.
In many cases, the role of given node is uncharacterised and we would seek to discover latent relationships through methods such as community detection.
The basic premise of community detection is that detecting dense topological sub-graphs allows one to uncover the function of vertices \cite{}.

In this paper, we consider the notion of relatedness to require additional meta-data, or vertex labels, that can be attributed to specific ontological definitions.
In many situations this information will be sparse or incomplete.
For example, in biological networks only a very small number of organisms have a high level of coverage in terms of functional annotation \cite{}.

The problem tackled in this paper can be formulated as follows:
Given a graph made up of vertices and edges $G = (V, E)$, we formally ask the question; \textit{How related is a given vertex to a given query set?}
This question assumes that a given query set is formally related, in practice, however, this may not be the case.
Consequently we also use our approach to ask another question; \textit{ How related are a set of query vertices?}

\section{Exploiting the modularity query space}
In order to characterise community structure, one of the most popular approaches is to use modularity maximisation.
The modularity quality function of a partition on a graph is given by the following equation \cite{newman2004}
\begin{equation}\label{eq:modularity}
  Q = \frac{1}{2m}\sum_{i,j} \left[A_{ij} - \frac{k_i k_j}{2m}\right]\delta(c_i, c_j),
\end{equation}
where $m$ is the number of edges in the network, $A_{ij}$ is the binary variable indicating the adjacency of nodes $i$ and $j$, $k_i$ is the degree of a vertex, $c_i$ indicates the community of a given vertex and $\delta(c_i, c_j)$ is the Kronecker delta such that $\delta(c_i, c_j) = 1$ if $c_i = c_j$ and $0$ otherwise.
As a combinatorial optimisation problem, there are many different algorithmic approaches to finding high values of $Q$.

@@

In our work, instead of seeing this modular search space as a flaw we consider each high value partition to be information about latent relationships between vertices inferred through the topology of the network.
In the parlance of the computational and information sciences, we consider the mapping of this search space to be an \textit{index} analogous to search algorithms.
Whilst methods based on simulated annealing can be used to guarantee full coverage of the network, the following section describes a method adapted from the greedy agglomerative Louvain algorithm \cite{blondel2008fast}.

@@

\subsection{Generating the search index}
In order to cover the space of high modularity partitions, randomly generated starting partitions are computed with a random cut set.
To achieve this each edge is either placed inside the cut set or not as the result of an independent Bernoulli trial. 
Each random partition is used as the starting partition for the greedy louvain process.
In principle, any search exploration procedure, such as simulated annealing \cite{GuimeraNature2005} could be used.
The Louvain algorithm is selected as it is fast, running in $O(n \log n)$ time complexity \cite{blondel2008fast}, and because it is a greedy algorithm is is guaranteed to stop after finding a locally maximal solution.

@@

\subsection{Measuring the quality of relationships} \label{sec:expansion}
Given a query of vertices, the relatedness to other vertexes in a network is quantifiable by the fraction of times they are clustered with the query set, given the set of high quality partitions.
Formally, this can be expressed in terms of the \textit{expansion score} of a given vertex,
% \begin{equation} \label{eq:mu_score}
% \mu_i(S) = \frac{1}{|\mathcal{P}| |S - i|} \sum_{P \in \mathcal{P}} \sum_{j \in S - i} \delta(c^{P}_{i}, c^{P}_{j}),
% \end{equation}
\begin{equation} \label{eq:mu_score}
\mu_i(S) = \frac{1}{|\mathcal{P}|} \sum_{P \in \mathcal{P}} \delta(c^{P}_i, c^{P}_S),
\end{equation}
where $S$ denotes a query set, $P$ is a given partition in the space of all high quality partitions $\mathcal{P}$, $c^{P}_{i}$ indicates the partition vertex $i$ is contained in within partition $P$ and
$\delta(u, v)$ is the Dirac delta function that equals 1 if are the same cluster and $0$ otherwise, where $c^{P}_S$ is given by,
\begin{equation}
 c^{P}_S = \argmax_{C \in P} |C \cap S|,
\end{equation}
or the largest intersecting cluster with the query set, in partition $P$.
Using the largest intersecting community with $S$ is both computationally favourable for computing $mu_i$ for all $i$ in $V$ and allows the query set to contain potentially spurious query nodes.
Where $\mu_i(S) = 1$ the partition space indicates that a given vertex is always partitioned in the same group as the query set.
In the case $\mu_i(S) = 0$ the vertex $i$ never appears in the same cluster as the largest query set.
We define $\mu_i(S)$ for all vertices in the network, including those in $S$.
In many cases, a query set will not be fully represented by the partitions found within the network, this is further elaborated in the following section.

@@

\section{Discussion}
The semi-supervised method for vertex classification presented in this work has shown to have good results on both synthetic benchmarks and real-world datasets.
Interestingly, this method is capable of correctly classifying communities with only a small number of seed query vertexes.
These results show that the community query method could be used as a powerful exploratory tool in network analysis.

The fact that the method is able to uncover small protein complexes seems to contradict the principle that modularity maximisation algorithms have a resolution limit \cite{}.
This may be due to the fact that
We do note that, where communities are very small, any approach will extremely sensitive to false positive and false negative results.
This should be considered when using this method as an exploratory tool.

@@

This allows the use of a single node to find related vertices, in real networks the results appeared to have a very good level of accuracy with average AUC of ROC curves above $0.9$.
In a practical context, however, this should not be interpreted as uncovering the community structure as this includes many overlapping communities for which the node is a member.

% \section{Related work}
% \label{sec:related_work}
% This work relates very strongly to the idea of local community detection, more specifically the idea of \textit{seed set expansion}.
% Here, a given seed set is created a random walks are analysed to find clearly related communities of vertices.
% One of the most common approaches to finding related vertices in a network is the random walk with restart (RWR) \cite{can2005analysis, kohler2008walking}.
% This approach has been applied in fields as diverse as recommender systems and the detection of potential drug targets \cite{chen2012drug}.
% In RWR the relatedness of any pair of vertices can be seen as the probability of a particle traversing the graph starting at a given vertex and ending at another.
% The restart aspect of the random walk can be thought of as the probability of the walker teleporting back to the start vertex with some none zero probability. 
% The higher the probability of the walker ending up at a given vertex, the more likely it is that the two vertices are related.
% 
% Conceptually, RWR is very similar to the method presented in this paper given that the user has a given query.
% One can thing of the RWR probability as analogous to the value of $\mu_i(S)$ presented above.
% However, the RWR value is based only on a single vertex as a query set where the approach presented in this work requires many vertices associated with a given label for it to be readily applicable.
% 
% Many existing method are based on the idea of a locally dense subgraph containing \textit{all query nodes} \cite{}.
% In contrast, the query approach presented here does not require the queries to be a self contained sub-graph.
% Indeed, queries can contain spurious nodes that are topologically distinct from one another - the result is that the either $q(S)$ score for the query will be very low and insignificant, or the spurious nodes will be ignored in the final query set.
% In user facing domains it is highly likely that very large query sets do not form isolated topologies.
% With Conventional methods some ``cleaning up'' of the underlying queries is often required to gather any meaningful expansion.
% 
% Whilst modularity maximisation is used for the set of global partitions, this approach is distinct from local modularity based approaches \cite{}.
% A limitation of this approach compared with localised methods is that the entire dataset is required.
% However, the objective is somewhat different as the approach presented here relies on high quality meta-data labels for queries.
% In this sense, the approach should be considered closer to semi-supervised \textit{classification} than unsupervised \textit{clustering}.
% 
% In the field of community detection, a number of very recent articles have focused on using metadata to improve the results of community detection approaches.
% 
% %TODO: Discuss citations of metadata based community detection - Newman-Clauset, Jure Lesovec, other citations in newman paper.
% 
% These algorithms, however, are distinct from the approach taken here as the metadata is not used in the module discovery process.
% Furthermore, the results in this work attempt to explicitly label unlabelled data and only require a relatively small number of labels to operate in such a fashion.
% In contrast,  the recent approach by Newman and Clauset \cite{}, for example, uses examples in which practically the entire network contains labels which is less useful from the perspective of label discovery.
% However, these methods are vastly superior to the work presented here when considering the research question of whether a labelling scheme (such as demography in a social network) accurately describes the structure of the network.

@@

However, this approach requires the community landscape to contain many local maxima, a property likely shared by many real networks.
Similarly, the method presented here requires both some labelled data and the labels to be represented well within the topology of the underlying network.
The approach presented here differs from other ensemble approaches in that the objective is to provide a probabilistic framework for label classification.
This approach performs extremely well on both synthetically generated networks and real-world ground truth communities with relatively small sets of labels.

% Furthermore, we extended the use of this framework to allow quality measurements of selected labellings and similarity comparrisons between data.

>>>>

% \author{John King}
% \affiliation{%
%   \institution{School of Mathematical Sciences}
%   \streetaddress{University of Nottingham}
%   \city{Nottingham}
%   \country{United Kingdom}
%   \postcode{NG7 2RD}
% }
% \email{john.king@nottingham.ac.uk}

\begin{abstract}
Uncovering latent community structure in complex networks is a field that has received an enormous amount of attention.
Unfortunately, whilst potentially very powerful unsupervised methods for uncovering labels based on topology alone has been shown to have several difficulties.
For example, the search space for module extraction approaches appears to be extremely glassy, with many high valued solutions that lack any real similarity to one another.
However, in this paper we argue that this is not a flaw with the modularity maximisation algorithm but, rather, information that can be used to aid the context specific classification of functional relationships between vertices.
Formally, we present an approach to generating a high value modularity consensus space for a network, based on the space of locally optimal modular partitions.
This is then used as an approach to uncover latent relationships between sets initial query sets.
The methods developed in this paper are applied to biological and social datasets with ground-truth label data, with a small number of examples used as seed sets to uncover relationships.
When tested on both real and synthetic datasets our method achieves extremely high levels of classification accuracy in a context specific manner.
Furthermore, the approach can be applied in distributed environments potentially allowing it to scale to very large networks.
\end{abstract}

@@

A fundamental issue at the heart of machine learning methods applied to large scale datasets is the ability to correctly identify classes of related objects in an unsupervised manner.
In network science, this methodology is often referred to as \textit{community} detection, due to the intuitive analogy to the notion of social groupings \cite{fortunato2010community}.
Many algorithms exist to solve this problem \cite{fortunato2016community}, yet initial starting conditions or different optimisation strategies may result in conflicting results even when the same objective function is being maximised \cite{good2010performance}.
In this paper, we develop an intuitive method to use the uncertainty amongst a high number of near optimal solutions to measure context sensitive relationships between small sets of labelled vertices.
This approach can be based on labels that are not first neighbours in order to find other potentially related vertices.

The number and size of communities is, generally, not known \textit{a priori}, and the problem has been shown to be NP-hard \cite{npHardModularity}.
The work of Good \textit{et al.} \cite{good2010performance} recently highlighted that the popular modularity maximisation algorithm has a highly ``glassy'' search space.
In this situation there are many locally optimal partitions that bear little to no resemblance to each other by measure of mutual information.
This allows greedy optimisation algorithms \cite{blondel2008fast} to trivially find solutions that score extremely high values of modularity.
In order to solve this issue, certain approaches use a consensus based approach to clustering, combining many high value partitions into a given median partition \cite{lancichinetti2012consensus}.

The use of community detection is widespread.
For example, core goal in systems biology is to characterise the function and functional relationships between genes, proteins or metabolites within a larger network \cite{girvan2002community}.
In many situations, only the role of a small number of genes is known, with much of the annotation for a given organism being computed through naive homology information that ignores the role of a gene within a wider context.
The advent of high throughput experimental datasets has allowed the construction of genome scale networks, leading to the observation of non-trivial topological properties such as densely connected clusters \cite{ArabidopsisConsortium2011}.
These densely connected clusters are widely believed to be associated with specific function, such as multi-protein complexes or biochemical pathways.

@@

In this paper, we do not seek to find a single ``best'' partition, either overlapping or not.
Instead, we use the large number of highly modular solutions to form the index for a search query system.
In essence, this is a method of semi-supervised learning that attempts to find items related given labelled sets of vertices using topology alone.
Each high value partition, if statistically more modular than random, can be treated as information about the relationships between vertices.
As the objective of community detection approaches is to relate information, it is assumed that some labelled meta-data can be used to find unlabelled, potentially related vertices.

We propose an algorithm that pre-computes an index of clusterings for a given complex network, based on the fast greedy Louvain algorithm \cite{blondel2008fast}, used in a distributed manner.
The detected clusters then form the basis of a searching algorithm that allows one to compute the relatedness of subsets of nodes.
The querying method is a polynomial time algorithm that could be trivially adapted to form the basis of many user facing applications.
This approach is applied to social and protein-protein interaction networks with good quality ground truth labels.

\section{The multi-vertex classification problem}
The intuitive notion that the structure of a vertex's connections gives insight into its function is a fundamental basis for research in network science.
In many cases, the role of given node is uncharacterised and we would seek to discover latent relationships through methods such as community detection.
The basic premise of community detection is that detecting dense topological sub-graphs allows one to uncover the function of vertices \cite{fortunato2010community}.

In this paper, we consider the notion of relatedness to require additional meta-data, or vertex labels, that can be attributed to specific ontological definitions.
In many situations this information will be sparse or incomplete.
For example, in biological networks only a very small number of organisms have a high level of coverage in terms of functional annotation \cite{bassel2012systems}.

The problem tackled in this paper can be formulated as follows:
Given a graph made up of vertices and edges $G = (V, E)$, and a query set $S \subset V$, we formally ask the question; \textit{How related is a given vertex to $S$?}
This question assumes that a given query set is formally related.
In practice, this is likely not the case for most subsets of $V$.
Consequently we also use our approach to ask another question; \textit{How well related is $S$?}
In order to answer these questions we focus on the set of high valued partitions of a given network detectable with the well known modularity maximisation algorithm.

\section{Exploiting the modularity query space}
To characterise latent community structure, one of the most popular approaches is to use modularity maximisation.
The modularity quality function of a partition on a graph is given by the following equation \cite{newman2004}
\begin{equation}\label{eq:modularity}
  Q = \frac{1}{2m}\sum_{i,j} \left[A_{ij} - \frac{k_i k_j}{2m}\right]\delta(c_i, c_j),
\end{equation}
where $m$ is the number of edges in the network, $A_{ij}$ is the binary variable indicating the adjacency of nodes $i$ and $j$, $k_i$ is the degree of a vertex, $c_i$ indicates the community of a given vertex and $\delta(c_i, c_j)$ is the Kronecker delta such that $\delta(c_i, c_j) = 1$ if $c_i = c_j$ and $0$ otherwise.
As a combinatorial optimisation problem, there are many different algorithmic approaches to finding high values of $Q$.

@@

In this work, we consider each high value partition to be information about latent relationships between vertices inferred through the topology of the network.
This approach, in and of itself is not unique, as there have been previous approaches that use the consensus of an ensemble of clusters to create high quality overlapping clustering of networks \cite{lancichinetti2012consensus}.
Such an approach, whilst well principled, is a context insensitive view of the modular structure of a graph.

The objective, then, is to use the disagreement between the set of highly modular partitions as information; that is to say, to infer the probability that sets of vertices are contained within the same cluster.
Whilst methods based on simulated annealing can be used to guarantee full coverage of the network, the following section describes a method adapted from the greedy agglomerative Louvain algorithm \cite{blondel2008fast}.

@@

In order to cover the space of high modularity partitions, randomly generated starting partitions are computed with a random cut set.
To achieve this each edge is either placed inside the cut set or not as the result of an independent Bernoulli trial. 
Each random partition is used as the starting partition for the greedy Louvain process.
In principle, any search exploration procedure, such as simulated annealing \cite{GuimeraNature2005} could be used.
The Louvain algorithm is selected as it is fast, running in $O(n \log n)$ time complexity \cite{blondel2008fast}, and because it is a greedy algorithm is is guaranteed to stop after finding a locally maximal solution.

@@

\subsection{Measuring the quality of relationships} \label{sec:expansion}
Given a query of vertices, the relatedness to other vertexes in a network is quantifiable by the fraction of times they are clustered with the query set, given the set of high quality partitions.
Formally, this can be expressed in terms of the \textit{expansion score} of a given vertex,
\begin{equation} \label{eq:mu_score}
\mu_i(S) = \frac{1}{|\mathcal{P}| |S| } \sum_{P \in \mathcal{P}} \sum_{j \in S} \delta(c^{p}_i, c^{p}_j),
\end{equation}
where $S$ denotes a query set, $P$ is a given partition in the space of all high quality partitions $\mathcal{P}$, $c^{p}_{i}$ indicates the partition vertex $i$ is contained in within partition $P$ and
$\delta(u, v)$ is the Dirac delta function that equals 1 if $c^{p}_i$ and  $c^{p}_j$ are the same cluster and $0$ otherwise.
As a simple example, for a pair of vertices $i$ and $S$ such that $S = {j}$ we would consider $\mu_i$ to be the number of times $i$ and $j$ appear in the same cluster, given an ensemble of network clusterings.
We define $\mu_i(S)$ for all vertices in the network, including those in $S$.
However, for the case where $i$ is in $S$ we, instead, consider the value $\mu_i(S - i)$ to remove bias.
In many cases, a query set will not be fully represented by the partitions found within the network, this is further elaborated in the following section.

@@

\section{Discussion}
The semi-supervised method for vertex classification presented in this work has shown to have good results on both synthetic benchmarks and real-world datasets.
Interestingly, this method is capable of correctly classifying communities with only a small number of seed query vertexes.
These results show that this query method could be used as a powerful exploratory tool in network analysis.

The fact that the method is able to uncover small protein complexes seems to contradict the principle that modularity maximisation algorithms have a resolution limit \cite{fortunato2007resolution}.
Whilst this appears to be the case it is important to not that the resolution limit applies to a single partition of space.
Further work is needed to investigate why small communities are still detectable.
However, we speculate that is likely due to the fact that the co-classification of vertices between different partitions remains fairly tolerant to changes.
I.e. whilst the large communities they reside in changes significantly, the small cluster of nodes is always clustered in the same community, regardless of the partition.
We do note that, where communities are very small, any approach will extremely sensitive to false positive and false negative results.
As such, this should be considered when using any method of this form as an exploratory tool.

@@

\section{Related work}
\label{sec:related_work}
This work relates very strongly to the idea of local community detection, more specifically the idea of \textit{seed set expansion} \cite{gleich2012vertex}..
Here, a given seed set is created a random walks are analysed to find clearly related communities of vertices.
One of the most common approaches to finding related vertices in a network is the random walk with restart (RWR) \cite{can2005analysis, kohler2008walking}.
This approach has been applied in fields as diverse as recommender systems and the detection of potential drug targets \cite{chen2012drug}.
In RWR the relatedness of any pair of vertices can be seen as the probability of a particle traversing the graph starting at a given vertex and ending at another.
The restart aspect of the random walk can be thought of as the probability of the walker teleporting back to the start vertex with some none zero probability. 
The higher the probability of the walker ending up at a given vertex, the more likely it is that the two vertices are related.

Conceptually, RWR is very similar to the method presented in this paper given that the user has a given query.
The RWR probability as analogous to the value of $\mu_i(S)$ presented above.
Further investigation needs to be conducted into how similar local community based approaches, such as random walks, compare with this method.

Many existing method are based on the idea of a locally dense subgraph containing \textit{all query nodes} \cite{benson2016higher}.
In contrast, the query approach presented here does not require the queries to be a self contained sub-graph.
Indeed, queries can contain spurious nodes that are topologically distinct from one another - the result is that the either $q(S)$ score for the query will be very low and statistically insignificant, or the spurious nodes will be ignored in the final query set.

In the field of community detection, a number of very recent articles have focused on using metadata to improve the results of community detection approaches.
These algorithms, however, are distinct from the approach taken here as the metadata is not used in the module discovery process.
Furthermore, the results in this work attempt to explicitly label unlabelled data and only require a relatively small number of labels to operate in such a fashion.
In contrast,  the recent approach by Newman and Clauset \cite{newman2016structure}, for example, uses examples in which practically the entire network contains labels which is less useful from the perspective of label discovery.
However, these methods generally consider if a labelling scheme (such as demography in a social network) accurately describes the structure of the network.

@@

However, this approach requires the community landscape to contain many local maxima, a property likely shared by many real-world, heterogeneous networks.
Similarly, the method presented here requires both some labelled data and the labels to be represented well within the topology of the underlying network.
The approach presented here differs from other ensemble approaches in that the objective is to provide a probabilistic framework for label classification.
This approach performs extremely well on both synthetically generated networks and real-world ground truth communities with relatively small sets of labels.

This work presents a number of interesting potential future avenues for research, such as observing how query sets change in time dynamic or multi-scale networks.
Similarly, further analysis could be conducted to test how large the set of high value partitions needs to be, and how applicable this approach can be to very large graphs.
